---
title: "p8105_hw1_jf3355"
author: "Jiahao Fan"
date: "9/26/2021"
output: github_document
---
```{r,include=FALSE}
library(tidyverse)
```
#Problem 1

This problem is intended to emphasize variable types and introduce coercion; some awareness of how R treats numeric, character, and factor variables is necessary for working with these data types in practice.

Create a data frame comprised of:

a random sample of size 10 from a standard Normal distribution
a logical vector indicating whether elements of the sample are greater than 0
a character vector of length 10
a factor vector of length 10, with 3 different factor “levels”
```{r}
set.seed(1)
data_frame = tibble(
  sample = rnorm(10),
  vec_logical = sample > 0,
  vec_char = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  vec_factor = factor(c("Large", "Large", "Large", "Medium", "Medium", "Medium", "Small", "Small", "Small", "Small"))
)

#check the data frame
data_frame

#Try to take the mean of each variable in your dataframe. What works and what doesn’t?

mean(pull(data_frame, sample))
#it works
mean(pull(data_frame, vec_logical))
#it works
mean(pull(data_frame, vec_char))
#it doesn't work
mean(pull(data_frame, vec_factor))
#it doesn't work
#this is because `mean()` function doesn't support these two types of variable.
```
#In some cases, you can explicitly convert variables from one type to another. Write a code chunk that applies the as.numeric function to the logical, character, and factor variables (please show this chunk but not the output). What happens, and why? Does this help explain what happens when you try to take the mean?
```{r, eval=FALSE}
as.numeric(pull(data_frame, vec_logical))
as.numeric(pull(data_frame, vec_char))
as.numeric(pull(data_frame, vec_factor))

#The logical vector and the factor vector was converted successful. In the logical vector, TURE values are converted to 1,the FALSE values are converted to 0. In the factor vector, the levels were converted to numeric value 1，2，3. The character vector wasn't converted to numbers. The mean of the the logical vector tells us that how likely the sample is true; the character values do not have intrinsic numeric value and does not have a mean;the factor vector does not have a mean even though the levels can be converted numeric because levels are similar to ranks,so the mean has no numerical meaning.
```



#Problem2
```{r}
data("penguins", package = "palmerpenguins")
```

#Write a short description of the penguins dataset (not the penguins_raw dataset) using inline R code, including:

#the data in this dataset, including names / values of important variables
```{r}
str(penguins)
```
#The penguins dataset is a compilation of observations of penguin species (`r paste(levels(penguins$species), collapse = ", ")`) on the islands of `r paste(levels(penguins$island), collapse = ", ")` from `r min(penguins$year)` - `r max(penguins$year)`. Bill length, bill depth, flipper length, body mass,sex were variables that were captured. 

the size of the dataset (using nrow and ncol)
```{r}
size = nrow(penguins) * ncol(penguins)
size
```
#the mean flipper length
```{r}
round(mean(pull(penguins,flipper_length_mm), na.rm = TRUE))
```

#Make a scatterplot of flipper_length_mm (y) vs bill_length_mm (x); color points using the species variable (adding color = ... inside of aes in your ggplot code should help).

#Export your first scatterplot to your project directory using ggsave.
```{r}
ggplot(penguins, aes(x=bill_length_mm, y=flipper_length_mm, color = species)) +
    geom_point() +
    ggtitle("Bill Length vs flipper Length")

ggsave("scatter_plot.pdf", height=6, width = 4)
```




